### 2017-04-05 paper/evaluation.tex
fixed legend

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.
From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with the parallel execution modes \ForkSeq{} and
\ParClassParMeth{} enabled by default.
Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
``Group'' indicates the test cost group (see
Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
name of the project, the column ``\# of modules'' indicates the number
of modules with tests in the default execution, and the column
``Mode'' indicates the corresponding parallelization mode.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Apache Flink & 74 & \ForkSeq{} \\%
        Medium & BounceStorage Chaos HTTP Proxy & 1 & \ParClassSeqMeth{}\\%
        Medium & Hazelcast Jet & 7 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        Medium & Spotify Helios & 8 & \ForkSeq{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{figure}

@@

% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   &JenkinsCI Gerrit Trigger Plugin& 1 & \ForkSeq\\%
        Medium &Bouncestorage Chaos Http Proxy & 1 & C2\\%
        Medium &Javaslang & 1 & C3\\%
        Medium &Apache Flink & 1 &\ForkSeq\\%
        Medium &Apache Logging Log4J2 & 3 & \ForkSeq{}\\%
        Medium &Google Cloud Platform DataflowJavaSDK & 1 & C3\\%
        Medium &Hazelcast Jet & 1 & \ForkSeq\\%
        Medium &Jankotek MapDB & 1 & C3\\%
        Medium &Mapstruct & 1 & \ForkSeq\\%
        Medium &Spotify Helios & 3 & \ForkSeq\\%
        \bottomrule%
    \end{tabular}}
    \caption{\Fix{legend}}
    \label{tab:inspection-table}
\end{figure}
%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}

>>>>

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.
From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with the parallel execution modes \ForkSeq{}, \ParClassSeqMeth{} and
\ParClassParMeth{} enabled by default.
Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
``Group'' indicates the test cost group (see
Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
name of the project, the column ``\# of modules'' indicates the number
of modules with tests in the default execution, and the column
``Mode'' indicates the corresponding parallelization mode.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Apache Flink & 74 & \ForkSeq{} \\%
        Medium & BounceStorage Chaos HTTP Proxy & 1 & \ParClassSeqMeth{}\\%
        Medium & Hazelcast Jet & 7 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        Medium & Spotify Helios & 8 & \ForkSeq{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{figure}

@@

% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   &JenkinsCI Gerrit Trigger Plugin& 1 & \ForkSeq\\%
        Medium &Bouncestorage Chaos Http Proxy & 1 & C2\\%
        Medium &Javaslang & 1 & C3\\%
        Medium &Apache Flink & 1 &\ForkSeq\\%
        Medium &Apache Logging Log4J2 & 3 & \ForkSeq{}\\%
        Medium &Google Cloud Platform DataflowJavaSDK & 1 & C3\\%
        Medium &Hazelcast Jet & 1 & \ForkSeq\\%
        Medium &Jankotek MapDB & 1 & C3\\%
        Medium &Mapstruct & 1 & \ForkSeq\\%
        Medium &Spotify Helios & 3 & \ForkSeq\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with parallelization configurations in build files.}
    \label{tab:inspection-table}
\end{figure}
%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}
